formula1

### 2020-05-21 inst/formula1.Rmd
give proflike() a 'relative' argument

```{r,doproflikn,cache=TRUE}
H9
maxp(H9)
p <- seq(from=0.11,to=0.13,len=50)
u <- profsupp(H9,"Hamilton",p,n=14)
plot(p,u)
```

>>>>

```{r,doproflikn,cache=TRUE}
H9
maxp(H9)
p <- seq(from=0.11,to=0.13,len=50)
u01 <- profsupp(H9,"Hamilton",p,n=01)
plot(p,u01)
u20 <- profsupp(H9,"Hamilton",p,n=20)
plot(p,u20)
u50 <- profsupp(H9,"Hamilton",p,n=50)
plot(p,u50)
```
